---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ellipsis

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/ellipsis)](https://cran.r-project.org/package=ellipsis)
[![Codecov test coverage](https://codecov.io/gh/r-lib/ellipsis/branch/master/graph/badge.svg)](https://codecov.io/gh/r-lib/ellipsis?branch=master)
<!-- badges: end -->

Adding `...` to an S3 generic allows methods to take additional arguments, but it comes with a big downside: any misspelled or extraneous arguments will be silently ignored. This package explores an approach to making `...` safer, by supply a function that a generic can use to warn if any elements of `...` were not evaluated.

In the long run, this code is likely to live elsewhere (maybe R-core might be interested in making it part of base R). This repository tracks the current state of the experiment.

Thanks to [Jenny Bryan](http://github.com/jennybc) for the idea, and [Lionel Henry](http://github.com/lionel-) for the heart of the implementation.

## Installation

Install the released version from CRAN:

```{r, eval = FALSE}
install.packages("ellipsis")
```

Or the development version from GitHub:

```{r, eval = FALSE}
devtools::install_github("r-lib/ellipsis")
```

## Example

`safe_median()` works like `median()` but warns if any elements of `...` are never evaluated

```{r example}
library(ellipsis)
x <- c(1:10, NA)

safe_median(x)
safe_median(x, TRUE)
safe_median(x, na.rm = TRUE)
safe_median(x, na.mr = TRUE)
```
