---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ellipsis

Adding `...` to a function specification usually comes with a big downside: any mispelled or extraneous arguments will be silently ignored. This package explores an approach to making `...` safer, by inspecting its contents and warning if any elements were not evaluated.

## Installation

``` r
devtools::install_gituhb("hadley/ellipsis")
```

## Example

ellipsis comes with two functions that illustrates how we can make functionals (which pass `...` to another argument) and S3 generics (which pass `...` on to their methods) safer. `safe_map()` and `safe_median()` warn if you supply arguments that are never evaluated.

```{r example}
library(ellipsis)

x <- safe_map(iris[1:4], median, na.mr = TRUE)
x <- safe_map(iris[1:4], median, na.rm = TRUE)
x <- safe_map(iris[1:4], median, 2)
x <- safe_map(iris[1:4], median, 2, 3)

x <- safe_median(1:10)
x <- safe_median(1:10, FALSE)
x <- safe_median(1:10, na.rm = FALSE)
x <- safe_median(1:10, na.mr = TRUE)
```

## Limitations

Currently combining a safe functional with a safe S3 generic is rather noisy

```{r}
x <- safe_map(iris[1:4], safe_median, na.mr = TRUE)
```

