---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ellipsis
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

Adding `...` to a function specification usually comes with a big downside: any mispelled or extraneous arguments will be silently ignored. This package explores an approach to making `...` safer, by inspecting its contents and warning if any elements were not evaluated.

In the long run, this code is likely to live elsewhere. This repository tracks the current state of the experiment.

## Installation

``` r
devtools::install_gituhb("hadley/ellipsis")
```

## Example

ellipsis comes with two functions that illustrates how we can make functionals (which pass `...` to another argument) and S3 generics (which pass `...` on to their methods) safer. `safe_map()` and `safe_median()` warn if you supply arguments that are never evaluated.

```{r example}
library(ellipsis)

x <- safe_map(iris[1:4], median, na.mr = TRUE)
x <- safe_map(iris[1:4], median, na.rm = TRUE)
x <- safe_map(iris[1:4], median, 2)
x <- safe_map(iris[1:4], median, 2, 3)

x <- safe_median(1:10)
x <- safe_median(1:10, FALSE)
x <- safe_median(1:10, na.rm = FALSE)
x <- safe_median(1:10, na.mr = TRUE)
```

The top-level function handles all evaluation failures so that this only generates a single warning (not one warning from `safe_map()` and four from `safe_median()`)

```{r}
x <- safe_map(iris[1:4], safe_median, na.mr = TRUE)
```

