---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ellipsis

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/ellipsis)](https://cran.r-project.org/package=ellipsis)
[![Travis build status](https://travis-ci.org/r-lib/ellipsis.svg?branch=master)](https://travis-ci.org/r-lib/ellipsis)
[![Codecov test coverage](https://codecov.io/gh/r-lib/ellipsis/branch/master/graph/badge.svg)](https://codecov.io/gh/r-lib/ellipsis?branch=master)
<!-- badges: end -->

Adding `...` to a function is a powerful technique because it allows you to accept any number of additional arguments. Unfortunately it comes with a big downside: any misspelled or extraneous arguments will be silently ignored. This package provides tools for making `...` safer:

* `check_dots_evaluated()` warns if any components of `...` are not evaluated.
  This allows an S3 generic to state that it expects every input to be 
  evaluated.

* `check_dots_unnamed()` warns if any components of `...` are named. This
  allows you to collect arbitrary unnamed arguments, warning if the user
  misspells a named argument.

* `check_dots_unused()` warns if `...` is used. This allows you to use `...` to
  force the user to supply full argument names, while still warning if an
  argument name is misspelled.

Thanks to [Jenny Bryan](http://github.com/jennybc) for the idea, and [Lionel Henry](http://github.com/lionel-) for the heart of the implementation.

## Installation

Install the released version from CRAN:

```{r, eval = FALSE}
install.packages("ellipsis")
```

Or the development version from GitHub:

```{r, eval = FALSE}
devtools::install_github("r-lib/ellipsis")
```

## Example

`mean()` is a little dangerous because you might expect it to work like `sum()`:

```{r}
sum(1, 2, 3, 4)
mean(1, 2, 3, 4)
```

This silently returns the incorrect result because `mean()` has arguments `x` and `...`. The `...` silently swallows up the additional arguments. We can use `ellipsis::check_dots_used()` to check that every input to `...` is actually used:

```{r}
safe_mean <- function(x, ..., trim = 0, na.rm = FALSE) {
  ellipsis::check_dots_used()
  mean(x, ..., trim = trim, na.rm = na.rm)
}

safe_mean(1, 2, 3, 4)
```

